`flippant` -- An `R` package for the automated  analysis of dithionite scramblase

### 2015-09-19 inst/manuscript/manuscript.rmd
Draft intro to "Case Study" section;

#Case Study

>>>>

#Case Study
*Retinitis pigmentosa* is a degenerative disease of the retina, of which the 
majority of cases is linked to mutant forms of the G-protein coupled receptor 
rhodopsin [@mendes_mechanisms_2005]. Motivated by our recent discovery that 
opsin/rhodopsin has scramblase activity [@menon_opsin_2011;@goren_constitutive_2014],
we hypothesized that a class of enigmatic rhodopsin mutations, which are known
to cause *retinitis pigmentosa* yet do not display the commonly associated 
molecular phenotypes of impaired binding of retinal, folding and/or trafficking or 
transducin activation, may in fact be impacted in their scramblase activity.
This hypothesis was disproved when tested using the dithionite scramblase assay
among other techniques. However, the same set of experiments pointed at a defect 
in rhodopsin dimerization prior to insertion into liposomes, generating the new 
hypothesis that the mutations may cause disease by interfering with the highly 
ordered quarternary structure of the molecule in the retina 
[@ploier_perturbed_submitted].

`flippant`s capabilities are demonstrated here by reanalyzing the data underlying 
Figure 5b in @ploier_perturbed_submitted.
